The impact of forest management on the temperature sensitivity of organic matter

### 2024-08-06 Manuscript_draft/Draft.Rmd
Just a test
Updated Fig 1, with climate data. I made only one figure instead of one per site, it's busy but we would reduce the nr of figs if it worked.

---
title: "The impact of forest management on the temperature sensitivity of organic matter"
author: "Leticia Perez-Izquiero, Lorenzo Menichetti, Jorge Curiel-Juste, etc"
date: "2024-07-04"
output:
  bookdown::pdf_document2: default
  bookdown::html_document2: default
  #output: pdf_document
  #   citation_package: natbib
bibliography: references.bib
header-includes:
   - \usepackage[utf8]{inputenc}
   - \usepackage{textcomp}
   - \usepackage{amsmath}
   - \DeclareUnicodeCharacter{03C9}{$\omega$}  # Declare the Unicode character for omega
---

@@

# Abstract

@@

@@

## Sites microclimate
![Climatic parameters measured at the sites, plotted as data density of all measurements. Please notice thot not every time series covers the same period of time.](../Figures/climatedata.png){width=60%}

>>>>

---
title: "The impact of forest management on the temperature sensitivity of organic matter"
author: "Leticia Perez-Izquiero, Lorenzo Menichetti, Jorge Curiel-Juste, etc"
date: "2024-07-04"
output:
  bookdown::html_document2: default
  bookdown::pdf_document2: default
  #output: pdf_document
  #   citation_package: natbib
bibliography: references.bib
header-includes:
   - \usepackage[utf8]{inputenc}
   - \usepackage{textcomp}
   - \usepackage{amsmath}
   - \DeclareUnicodeCharacter{03C9}{$\omega$}  # Declare the Unicode character for omega
---

@@

# Abstract
TEST CHANGE

@@

## Soil C turnover is controlled by temperature and moisture

## Climate change will influence soil C turnover globally

@@

## Sites microclimate
<!-- ![Climatic parameters measured at the sites, plotted as data density of all measurements. Please notice thot not every time series covers the same period of time.](../Figures/climatedata.png){width=60%} -->
![Climatic parameters and respirations measured at the sites (mean values after loess interpolation with span = 0.5). Please notice thot not every time series covers the same period of time. Red shades = France, green shades = Romania, blue shades = Spain](../Figures/climatedata_means.png){width=60%}
